---
title: "Exponential Distribution Comparison to the Centeral Limit Theorem"
author: "Alex MacCalman"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
# Overview
In this project we will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. We will set  lambda = 0.2 for all of the simulations. We ill investigate the distribution of averages of 40 exponentials.
# Simulation
First we run a simulation, then calcualte the sample mean and variance and theoretcial mean and variance.  
```{r}
lambda <- 0.2
n <- 40
B <- 1000
set.seed(10)
sim <- matrix(rexp(n*B, lambda), B, n)
means <- apply(sim, 1, mean)
sampleMean <- mean(means)
theoreticalMean <- 1/lambda
sampleVar <- var(means)
theoreticalVar <- (1/lambda)^2/n
```
Next we display a histogram of the simulation and compare to the theoretical mean and variance with the sample mean and variance.  
```{r}
hist(means, col = "green", breaks = 30, main = "Histogram of exponential random variants with lambda = 0.2", xlab = "Sample Means of 40 Replications")
text(7,80, paste("Sample Mean = ", round(sampleMean, 4), "\n Theorectical Mean =", theoreticalMean, "\n", "\n Sample Variance = ", round(sampleVar, 4), "\n Theorectical Variance =", theoreticalVar))
```

In order to show that the distribution is approximatly normal, we overlay a density plot.
```{r}
hist(means, col = "blue", breaks = 30, main = "Histogram of exponential random variants compared with normal", xlab = "Sample Means of 40 Replications", prob = TRUE)
lines(density(means), col = "red")
```

Now we will calculate a 95% confidence interval for the exponential sample mean.  
```{r}
t.test(means)$conf.int
```

